---
title: "#TidyTuesday - Week 43"
subtitle: "Horror Movies"
author: '[Evan W Barba](https://github.com/ewbarba)'
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    lightbox: TRUE
    gallery: TRUE
    toc_depth: 2
  html_document:
    df_print: paged
    toc_depth: '1'
---

```{r}
#define packages desired
dependencies <- c("tidyverse", "plotly", "ggmap", "quantmod", "countrycode", "mgcv", "broom")

#check if pacakges are installed - load if so, install+load if not)
for (i in dependencies) {
  if (i %in% row.names(installed.packages())){
    eval(bquote(library(.(i))))
    message(paste("loaded package",i))
    }  else {
    install.packages(i)
    eval(bquote(library(.(i))))
  }
}

#This week's data is from the IMDB by way of Kaggle
horror_movies <-
  readr::read_csv(
    "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-22/horror_movies.csv"
  )

#register google api for lat long of filming locations
#register_google(key="<your key here (free @ https://developers.google.com/maps/documentation/maps-static/get-api-key)>", write=T)
```

Use google's api to gather lat and long of filming locations
```{r, message=FALSE}
locations <- horror_movies %>% filter(!is.na(filming_locations)) %>% mutate_geocode(.,filming_locations)
```

Data wringlin'
```{r}
horror_movies$currency <- gsub("[0-9,[:space:]]", "", horror_movies$budget) #strip currency
horror_movies$currency <- gsub("\\$", "USD", horror_movies$currency) #convert symbols to currency abbrvs
horror_movies$currency <- gsub("\\£", "GBP", horror_movies$currency)
horror_movies$currency <- gsub("\\€", "EUR", horror_movies$currency)
horror_movies$currency <- gsub("RUR", "RUB", horror_movies$currency) #1 RUB == 1000 RUR (Old Russian Ruble obsolete ca. 1998 - from coinmill.com) - change to get updated currency value
horror_movies$currency <- gsub("TRL", "TRY", horror_movies$currency) #1 TRY == 1000000 TRL (Old Turkis Lire obsolete ca. 2005 - from coinmill.com) - change to get updated currency value
horror_movies$currency <- str_remove_all(horror_movies$currency, "\\s") #compulsively remove the spaces
currencies <- unique(horror_movies$currency)[-1]#store uniq currency for conversions
horror_movies$run.time.num <- as.numeric(gsub(" min","", horror_movies$movie_run_time)) #get numeric value of runtimes
horror_movies$release_date <- as.Date(horror_movies$release_date, "%d-%b-%y") #release date formatting to Date class

#weed out the unrecognized currencies 
 for(i in currencies){
   tryCatch({
     getQuote(paste0(i,"USD","=X"))
     print(i)
   }, error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
 }

xchange.current <- getQuote(paste0(currencies, rep("USD", length(currencies)),"=X")) #get current exchange rate for currencies to USD, can replace USD with desired currency - only works when markets are open - change to getFX?
horror_movies$value.in.usd <- as.numeric(gsub("[^0-9]", "", horror_movies$budget))
#tail(getFX("SEK/USD", auto.assign = F),1)

#convert budgets to usd
for(i in 1:nrow(horror_movies)){
  if(!is.na(horror_movies$value.in.usd[i])){
    horror_movies$value.in.usd[i] <- horror_movies$value.in.usd[i]*xchange.current$Last[which(grepl(horror_movies$currency[i], substr(row.names(xchange.current),1,3)))]
  }
}

#adjust RUR to RUB
for(i in which(horror_movies$currency=="RUB")){
  horror_movies$value.in.usd[i] <- horror_movies$value.in.usd[i]/1000
}

#Adjust TRL to TRY
for(i in which(horror_movies$currency=="TRY")){
  horror_movies$value.in.usd[i] <- horror_movies$value.in.usd[i]/1000000
}

#Add region and continent information
horror_movies$region <- countrycode(sourcevar = horror_movies$release_country, origin = "country.name", destination = "region")
horror_movies$continent <- countrycode(sourcevar = horror_movies$release_country, origin = "country.name", destination = "continent")
```


```{r}
#generate figure
plot_ly(horror_movies,
        y=~review_rating,
        x=~log(value.in.usd),
        color=~continent,
        size = ~run.time.num,
        text = ~paste0('<b>',title,'</b>', '<br>','<br>',  
                      'Review rating: ', review_rating, '<br>',
                      'log(Budget) (in $USD): $', value.in.usd, '<br>',
                      'Run-time: ', movie_run_time, '<br>',
                      'Language: ', language,'<br>',
                      'Release Country: ', release_country)) %>%
  add_annotations(text = "Conintent Released",
                     xref = "paper",
                     yref = "paper",
                     x = 1.01, 
                     xanchor = "left",
                     y = .67,
                     yanchor = "top",
                     legendtitle = TRUE,
                     showarrow = FALSE) %>%
  
  layout(title="Log Transformed Budgets vs Reviews",
         yaxis = list(title = 'Review Rating'),
         xaxis = list(title = 'log(Budget) in $USD', position =0),
         legend = list(x=100,y=.5, text='title'),
          images = list(
          source = "https://media.istockphoto.com/photos/fog-background-picture-id845785528?k=6&m=845785528&s=612x612&w=0&h=VRNazaue6d8xtOBMnV01OV1bpsmo_TfsDVi84gXx278=",
           xref = "x",
           yref = "y",
           x= -10,
           y= 10,
           sizex = 40,
           sizey = 10,
           sizing = 'stretch',
           opacity = 0.4,
           
           layer='below'
        )
      )
```

>This figure shows the relationship between budget (log scale, converted to USD) and rating. Each maker is sized by runtime and colored by continental origin.

```{r}
locations$region <- countrycode(sourcevar = locations$release_country, origin = "country.name", destination = "region")
locations$continent <- countrycode(sourcevar = locations$release_country, origin = "country.name", destination = "continent")


g <- list(
  showland = TRUE,
  showlakes = TRUE,
  showcountries = TRUE,
  showocean = TRUE,
  countrywidth = 0.5,
  x=1,y=1,
  landcolor = toRGB("grey50"),
  lakecolor = toRGB("grey90"),
  oceancolor = toRGB("grey24"),
  projection = list(
    type = 'orthographic',
    rotation = list(
      lon = -100,
      lat = 40,
      roll = 0
    )
  ))

plot_geo(locations, locationmode = 'USA-states', sizes = c(1, 250),
         text = ~paste0('<b>',title,'</b>', '<br>','<br>',
                      'Filimg Location: ', filming_locations, '<br>',
                      'Review rating: ', review_rating, '<br>',
                      'Run-time: ', movie_run_time, '<br>',
                      'Language: ', language,'<br>',
                      'Release Country: ', release_country)) %>%
   add_annotations(text = "Conintent Released",
                     xref = "paper",
                     yref = "paper",
                     x = 1.01, 
                     xanchor = "left",
                     y = .67,
                     yanchor = "top",
                     legendtitle = TRUE,
                     showarrow = FALSE) %>%
  add_markers(
    x = ~lon,
    y = ~lat, 
    size = ~review_rating,
    color = ~continent) %>%
  layout(title = 'The World\'s Spookiest Places (if filming locations are an indicator)', geo = g,
         legend = list(x=100,y=.5))
         



```

>This plot displays all filming locations from the provided dataset. Each marker is sized by movie rating and colored by continent of release




#####Bonus I have not gotten to yet

#Using historical exchange rate data from https://fred.stlouisfed.org, gathered by Datopian (https://datahub.io/core)...not today
```{r}
xchangerate <- read_csv("https://pkgstore.datahub.io/core/exchange-rates/daily_csv/data/03e15e28c7eea87026fee299a8859e97/daily_csv.csv")
```


Determine number of listed cast
```{r}
horror_movies$num.listed.cast <- NA
for(i in 1:nrow(horror_movies)){
  horror_movies$num.listed.cast[i] <- length(str_split(horror_movies$cast[i], "\\|")[[1]])
  } 

```

```{r}
plot_ly(horror_movies,
        y=~review_rating,
        x=~release_date,
        size =~value.in.usd,
        color = ~run.time.num,
        text = ~paste0('<b>',title,'</b>', '<br>','<br>',  
                      'Review rating: ', review_rating, '<br>',
                      'log(Budget) (in $USD): $', value.in.usd, '<br>',
                      'Run-time: ', movie_run_time, '<br>',
                      'Language: ', language,'<br>',
                      'Release Country: ', release_country)) %>%
  add_trace(horror_movies,
            x=~release_date,
            y=~run.time.num,
            mode='line')
```